<!-- Specify the report's official name, goal & description. -->
# Row Counts
**Report Description**: This report helps monitor the activity and (partial) health of the databases.

```{r, echo=FALSE, message=F} 
#Set the chunks' working directory to the repository's base directory; this assumes the report is nested inside of two directories.
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -espeically one that uses file paths.
```
<!-- Point knitr to the underlying code file so it knows where to look for the chunks. -->
```{r, echo=FALSE, message=F}
# getwd()
opts_chunk$set(fig.width=12, 
               fig.height=3, 
               fig.path='FigureRmd/'
               )#, dpi=400)

options(width=120)
               
require(xtable)
require(scales)
pathSourceCode <- "./Reports/RowCountHistory/RowCountHistory.R"
read_chunk(pathSourceCode) 
```

<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r LoadPackages, echo=FALSE, message=FALSE}
```

<!-- Load any Global Functions declared in the R file.  Suppress the output. --> 
```{r DeclareGlobalFunctions, echo=FALSE, message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=FALSE, message=FALSE}
PrintTable <- function( dsTable ) {
  print(xtable(dsTable), type="html")
}
```
<!-- Load the dataset.   -->
```{r LoadDS, echo=F, results='hide', message=F}
```
<!-- Tweak the dataset.   -->
```{r TweakDS, echo=F, results='hide', message=F}
```

```{r ReportParameters, echo=FALSE}
# print(dirname(getwd()))
cat(paste0("This report covers records between ", min(dsLog$probe_date, na.rm=T), " and ",  max(dsLog$probe_date, na.rm=T), ".\n",
  "This report contains information from ", 
           comma(length(unique(dsLog$database))), " databases, ", 
           comma(length(unique(dsLog$table))), " tables, and ", 
           comma(nrow(dsLog)), " records."))

```

## Row Count of Each Table of Each Database
The table displays the number of records in each table, and how that count has increased or decreased since the last occasion the table was probed.

Below the table are line graphs that show the history of each database table.  The text above each line is the change since the last probe.

```{r RowCountTable, echo=FALSE}
```

```{r RowCountGraph, echo=FALSE, results='asis'}
```
